Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Tweak technology language; prefer "Web" to "internet".

New story modules can be incorporated by visiting an internet page in
connected deployments.  In disconnected deployments, new stories
might be distributed once a year on USB sticks, or shared among
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.

>>>>

New story modules can be downloaded from the Web in
connected deployments.  In disconnected deployments, new stories
might be distributed once a year on USB sticks or shared among
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.
